\ourtitle

### 2020-07-11 paper/article.tex
Update dissertation

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.65\linewidth]{../dissertation/rpd/img/diagram_architecture_en_vertical.png}}%
  }%
  \caption{The three main layers of the project.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{../code/musikla/musikla/examples/paper/concatenation2.png}}%
  }%
  \caption{Generated music sheet for concatenation\protect\footnotemark, audio version available \href{https://drive.google.com/open?id=1TP4lcul81s8iMCUFmD3HKnSpeftCzKT0}{\underline{here}}\protect\footnotemark.}
  \label{fig:concatenation}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{../code/musikla/musikla/examples/paper/repetition2.png}}%
  }%
  \caption{Generated music sheet for repetition, audio version available \href{https://drive.google.com/open?id=1IIm8PQkLsNFMK9MNSVubJSG6SP6KwhPL}{\underline{here}}\protect\footnotemark.}
  \label{fig:repetition}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{../code/musikla/musikla/examples/paper/parallel2.png}}%
  }%
  \caption{Generated music sheet for parallel, audio version available \href{https://drive.google.com/open?id=1ENTm3hZonYHyQIOgRZ8TQ1Qz-AfRLt2I}{\underline{here}}\protect\footnotemark.}
  \label{fig:parallel}
\end{figure}
\footnotetext{\url{https://drive.google.com/open?id=1ENTm3hZonYHyQIOgRZ8TQ1Qz-AfRLt2I}}

@@

\begin{lstlisting}[label={lst:fugue},caption={Example of repeating the same note},captionpos=t,abovecaptionskip=-\medskipamount]
fun fugue ( $subj, $resp ) => 
    ( $subj $resp | r ** $subj ( $subj + 7 ) );

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{../code/musikla/musikla/examples/paper/fugue.png}}%
  }%
  \caption{Generated music sheet for fugue example, audio version available \href{https://drive.google.com/file/d/1dIfvnhhKn73Vpp0W6ss6RLsv6PQ_HFTF/view}{\underline{here}}\protect\footnotemark.}
  \label{fig:fugue}
\end{figure}
\footnotetext{\url{https://drive.google.com/file/d/1dIfvnhhKn73Vpp0W6ss6RLsv6PQ_HFTF/view}}

>>>>

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.65\linewidth]{./img/diagram_architecture_en_vertical.png}}%
  }%
  \caption{The three main layers of the project.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{./img/concatenation2.png}}%
  }%
  \caption{Generated music sheet for concatenation\protect\footnotemark, audio version available \href{https://drive.google.com/open?id=1TP4lcul81s8iMCUFmD3HKnSpeftCzKT0}{\underline{here}}\protect\footnotemark.}
  \label{fig:concatenation}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{./img/repetition2.png}}%
  }%
  \caption{Generated music sheet for repetition, audio version available \href{https://drive.google.com/open?id=1IIm8PQkLsNFMK9MNSVubJSG6SP6KwhPL}{\underline{here}}\protect\footnotemark.}
  \label{fig:repetition}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{./img/parallel2.png}}%
  }%
  \caption{Generated music sheet for parallel, audio version available \href{https://drive.google.com/open?id=1ENTm3hZonYHyQIOgRZ8TQ1Qz-AfRLt2I}{\underline{here}}\protect\footnotemark.}
  \label{fig:parallel}
\end{figure}
\footnotetext{\url{https://drive.google.com/open?id=1ENTm3hZonYHyQIOgRZ8TQ1Qz-AfRLt2I}}

@@

\begin{lstlisting}[label={lst:fugue},caption={Using variables and functions to compose musical arrangements},captionpos=t,abovecaptionskip=-\medskipamount]
fun fugue ( $subj, $resp ) => 
    ( $subj $resp | r ** $subj ( $subj + 7 ) );

@@

\begin{figure}[ht]
  \centering
  {%
  \setlength{\fboxsep}{0pt}%
  \setlength{\fboxrule}{0pt}%
  \fbox{\includegraphics[width=.85\linewidth]{./img/fugue.png}}%
  }%
  \caption{Generated music sheet for fugue example, audio version available \href{https://drive.google.com/file/d/1dIfvnhhKn73Vpp0W6ss6RLsv6PQ_HFTF/view}{\underline{here}}\protect\footnotemark.}
  \label{fig:fugue}
\end{figure}
\footnotetext{\url{https://drive.google.com/file/d/1dIfvnhhKn73Vpp0W6ss6RLsv6PQ_HFTF/view}}
